Scalar Feedback based Joint Time-Frequency Precoder interpolation for MIMO-OFDM Systems

### 2019-10-11 paper/main.tex
Add changes

\subsection{Scalar Parametrization}
\label{givens}
The degrees of freedom in the $\bV_{i,t}$ matrices is smaller than the
number of real entries in the matrix because of the geometrical
structure between the columns of the matrix~\cite{4114278}. The
orthonormal matrix $\bV_{i,t}$ with $N_T$ rows and $N_R$ columns can be
decomposed as TODO
\begin{equation}
\textbf{V} = \Bigg[\prod_{k=1}^{N_{R}} \bD_{k} \big( \phi_{k,k},\ldots , \phi_{k,N_{R}} \big) \: \Bigg\{ \prod_{l=1}^{l=N_{T}-k} \bG_{N_{T}-l,N_{T} -l+1} \big( \theta_{k,l}\big) \Bigg\} \Bigg] \: \tilde{\bI}
\end{equation}
where $D_{k}$ is the diagonal matrix given as $D_{k}\big(\phi_{k,k},
\ldots, \phi_{k,N_T } \big)$ =  $\mbox{diag}\big( {\bf 1}_{k-1},
e^{j\phi_{k,k}},\ldots, e^{j\phi_{k,N_T }}  \big)$, ${\bf 1}_{k-1}$ is
represents  $k-1$ ones, and the $N_R \times N_T$ matrix $\tilde{\bI}$
= $\big[\bI_{N_R }, {\bf 0}_{N_T ,N_T -N_R }\big]^{T}$, and
\begin{equation}
G_{m-1,m}\big(\theta\big)  =
\begin{bmatrix}
I_{m-2} & & & \\
& \cos\theta & -\sin\theta & \\
& \sin\theta & \cos\theta & \\
& & & I_{t-m}
\end{bmatrix}
\end{equation}
Thus, for a $4 \times 2$ orthogonal matrix $\bV_{i,t}$, we have
\begin{align*}
  \bV_{i,t} & =
  \bD_{1}(\phi_{1,1},\ldots,\phi_{1,4})\bG_{3,4}(\theta_{1,1})
  \bG_{2,3}(\theta_{1,2}) \bG_{1,2}(\theta_{1,3})\times\\
& \bD_{2}(\phi_{2,2},\phi_{2,3},\phi_{2,4}) \bG_{3,4}(\theta_{2,1}) \bG_{2,3}(\theta_{2,2})\tilde{\bI}
\end{align*}
Here, $\phi_{k}$s are referred to as phases; their collection is given by $\Phi and $$\theta_{l}$s as rotation angles; their collection is given by $\Theta$. $\phi_k \in (-\pi, + \pi]$ is uniformly distributed
between the two extremes\cite{4114278}, while $\theta_l$
is distributed as
\begin{equation}
p(\theta) = 2l(\sin\theta)^{2l-1}\cos\theta, \theta \in \left[0, \frac{\pi}{2}\right) \mbox{ for } l = 1,2,\ldots,N_T -1
\end{equation}
The $\phi_k$ and $\theta_l$ are statistically independent, making this
representation useful for tracking them separately across time, as
explained in the following subsection. The total number of parameters
obtained from the decomposition of a complex orthogonal matrix
$N_{T} \times N_{R} $ is $N_{R}(2N_{T} - N_{R})$~\cite{4114278}. The
number of $\phi_i$ parameters is $N_{R}(2N_{T} - N_{R}-1)/2$ while the
number of $\theta$ parameters is $N_{T}(2N_{T} - N_{R}+1)/2$.
\begin{figure}
\includegraphics[width=0.5\textwidth]{images/new-adpm.pdf}
\caption{\label{fig:adpm-fig}Subcarriers which need to be quantized}
\label{ber_overvie}
\vspace{-5pt}
\end{figure}
% To exploit the interpolation of time \& frequency jointly at the transmitter, feedback bits are sent in an alternating fashion as shown in the figure.

>>>>

\subsection{Scalar Parametrization}
\label{givens}
The degrees of freedom in the $\bV_{i,t}$ matrices is smaller than the
number of real entries in the matrix because of the geometrical
structure between the columns of the matrix~\cite{4114278}. The
orthonormal matrix $\bV_{i,t}$ with $N_T$ rows and $N_R$ columns can be
decomposed as TODO
\begin{equation}
\textbf{V} = \left[\prod_{k=1}^{N_{R}} \bD_{k} \left( \phi_{k,k},\ldots , \phi_{k,N_{R}} \right) \:  \prod_{l=1}^{N_{T}-k} \bG_{N_{T}-l,N_{T} -l+1} \big( \theta_{k,l}\big)  \right] \: \tilde{\bI}
\end{equation}
where $D_{k}$ is the diagonal matrix given as $D_{k}\big(\phi_{k,k},
\ldots, \phi_{k,N_T } \big)$ =  $\mbox{diag}\big( {\bf 1}_{k-1},
e^{j\phi_{k,k}},\ldots, e^{j\phi_{k,N_T }}  \big)$, ${\bf 1}_{k-1}$ is
represents  $k-1$ ones, and the $N_R \times N_T$ matrix $\tilde{\bI}$
= $\big[\bI_{N_R }, {\bf 0}_{N_T ,N_T -N_R }\big]^{T}$, and
\begin{equation}
G_{m-1,m}\big(\theta\big)  =
\begin{bmatrix}
I_{m-2} & & & \\
& \cos\theta & -\sin\theta & \\
& \sin\theta & \cos\theta & \\
& & & I_{t-m}
\end{bmatrix}
\end{equation}
Thus, for a $4 \times 2$ orthogonal matrix $\bV_{i,t}$, we have
\begin{align*}
  \bV_{i,t} & =
  \bD_{1}(\phi_{1,1},\ldots,\phi_{1,4})\bG_{3,4}(\theta_{1,1})
  \bG_{2,3}(\theta_{1,2}) \bG_{1,2}(\theta_{1,3})\times\\
& \bD_{2}(\phi_{2,2},\phi_{2,3},\phi_{2,4}) \bG_{3,4}(\theta_{2,1}) \bG_{2,3}(\theta_{2,2})\tilde{\bI}
\end{align*}
Here, $\phi_{k}$s are referred to as phases; their collection is given
by $\Phi$ and $\theta_{l}$s as rotation angles; their collection is
given by $\Theta$. $\phi_k \in (-\pi, + \pi]$ is uniformly distributed
between the two extremes~\cite{4114278}, while $\theta_l$ is
distributed as
\begin{equation}
2l(\sin\theta_l)^{2l-1}\cos\theta_l, \theta_l \in \left[0, \frac{\pi}{2}\right) \mbox{ , } l = 1,2,\ldots,N_T -1
\end{equation}
The $\phi_k$ and $\theta_l$ are statistically independent, making this
representation useful for tracking them separately across time, as
explained in the following subsection. The total number of parameters
obtained from the decomposition of a complex orthogonal matrix
$N_{T} \times N_{R} $ is $N_{R}(2N_{T} - N_{R})$~\cite{4114278}. The
number of $\phi_i$ parameters is $N_{R}(2N_{T} - N_{R}-1)/2$ while the
number of $\theta$ parameters is $N_{T}(2N_{T} - N_{R}+1)/2$.
\begin{figure}
\includegraphics[width=0.5\textwidth]{images/new-adpm.pdf}
\caption{\label{fig:adpm-fig}Subcarriers which need to be quantized}
\label{ber_overvie}
\vspace{-5pt}
\end{figure}
% To exploit the interpolation of time \& frequency jointly at the transmitter, feedback bits are sent in an alternating fashion as shown in the figure.
